\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ahmad Alrai} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+967 775 968 918 \\ Sana'a, Yemen} 
\address{\href{https://ahmadalrai.com/}{ahmadalrai.com} \\ 
\href{mailto:ahmadhalraie@gmail.com}{ahmadhalraie@gmail.com} \\ 
\href{https://www.linkedin.com/in/ahmadalrai/}{linkedin.com/in/ahmadalrai} \\ 
\href{https://github.com/ahmadhrai}{github.com/ahmadhrai}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Software engineer with strong problem-solving skills and a proven track record of creating and designing software in test-driven environments. With 4+ years of experience in front-end web development, I am now seeking full-time full-stack roles to further leverage my skills in both client-side and server-side technologies.}


\end{rSection}


%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Networking Skills & Routing, Switching, Network Planning, Subnetting, System Administration\\
Programming Languages & C, C++, C\#, Java, JavaScript, PHP, Python, SQL, and learning Rust\\
Technologies and Frameworks & Git, Docker, Node.js, Express, React, Next.js, Flutter, and Nest.js\\
\end{tabular}\\
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Frontend Developer} \hfill Sep 2023 - Present\\
Revolution of Technical Solutions \hfill \textit{Sana'a, Yemen}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Made critical decisions regarding the tech stack (React, Material-UI) and architectural design for dynamic dashboards, optimizing performance, scalability, and user experience.
    \item Developed and maintained dynamic dashboards for multiple systems (Gateway, Fatoorah, Jood) with a focus on seamless integration with back-end services and ensuring intuitive, user-friendly interfaces.
    \item Managed code versioning through Git and Azure DevOps, ensuring smooth collaboration and efficient deployment pipelines across the team.
    \item Implemented Agile methodology, primarily using the SCRUM framework, to drive project execution, conducting daily stand-ups, sprint planning, and retrospectives to improve team collaboration and delivery efficiency.
 \end{itemize}

 \textbf{Full Stack Developer} \hfill Jan 2022 - Jun 2023\\
Light Foundation for Development \hfill \textit{Sana‘a, Yemen}
 \begin{itemize}
    \itemsep -3pt {}
    \item Built and maintained the organization's personal website using React and Next.js, while also managing and optimizing the Monitoring and Evaluation (M\&E) system for internal platforms.
    \item Developed and maintained both front-end and back-end systems using React, Next.js, Express, and Nest.js, ensuring scalable and functional digital infrastructure.
    \item Supported the organization’s technology initiatives by delivering timely updates and improvements across various platforms, while ensuring smooth communication with the team.
 \end{itemize}
 
\textbf{Unity Game Developer} \hfill Aug 2021 - Jan 2022\\
Arkadia Studio \hfill \textit{Sana‘a, Yemen}
 \begin{itemize}
    \itemsep -3pt {}
    \item Contributed to the design, development, and deployment of a 2D mobile game for Android and iOS platforms, collaborating closely with a cross-functional team to ensure high-quality game mechanics and a seamless user experience. 
    \item  Utilized Unity3D and C\# to implement gameplay systems, interactive UI components, and optimize performance across multiple devices, enhancing user engagement and game responsiveness. 
    \item Assisted in the integration of audio, character animations, and level design elements, helping to create an immersive and polished final product.
 \end{itemize}

\textbf{Full-stack Developer} \hfill Mar 2021 - Jul 2021\\
Ysys Co. \hfill \textit{Sana‘a, Yemen}
 \begin{itemize}
    \itemsep -3pt {}
    \item Developed a Loan Management System using Flutter, including features for loan tracking, repayment scheduling, and user account management. 
    \item Designed and implemented a Learning Management System (LMS) with integrated Flutter mobile application, supporting course delivery, user progress tracking, and interactive learning modules.
    \item Built a Transportation Management Mobile Application using Flutter, incorporating real-time tracking, route optimization, and driver-client communication tools. 
 \end{itemize}
 
\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Tabadul.} {Collaborated with a team in building a fully responsive and highly scalabe website that allows users to share and refurbish items using Next.js, Firebase, Git version control, ESLint. (\href{https://tabadul.vercel.app/}{Demo})}
\item \textbf{Khedma Handyman App.} {Built a handyman on demand, home repairing services application as a graduation project from LIU. Technologies used: PHP, Laravel, Firebase Dart \& Flutter. Could be explored in the following GitHub repositories (\href{https://github.com/AhmadHRai/KhedmaProjectLaravel}{Laravel}) (\href{https://github.com/AhmadHRai/KhedmaProjectFlutter}{Flutter})}
\item \textbf{Personal Portfolio.} {Designed and developed a responsive personal portfolio using Next.js and React, featuring project showcases, an interactive contact form, and SEO optimization. Visit my \href{https://ahmadalrai.com}{Portfolio}.}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Front-end Web Development Bootcamp}, \href{https://www.re-coded.com/}{Re:Coded}\hfill {Dec 2022 - May 2023}
 \begin{itemize}
    \itemsep -3pt {} 
     \item 6 Months of intensive project-based learning run by Re:Coded with Flatiron School's curriculum.
     \item Front End Web Development (HTML, CSS, JavaScript, React)
     \item Immersive coding with simulated client projects\\
 \end{itemize}



{\bf Bachelor of Computer Science \& Information Technology}, Lebanese International University \hfill {2019 - 2022}
Graduated with 3.97 GPA \smallskip \\
Relevant Coursework:
\begin{itemize}
    \itemsep -3pt {} 
    \item Networking, Security, IT Hardware, Windows Server
    \item Programming (C, Java), Mobile Programming (Java with Android Studio), AI
    \item Operation Management, Knowledge Management, E-business
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Extra-Curricular Activities SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Tutored in C language, Java, and Android programming at Lebanese International University.
    \item	Co-founder of the first Google Developers Student Club (GDSC) in Yemen (2019) and a core team member at Lebanese International University for two years. Actively organized events and host info sessions about various technology-related topics on the GDSC Community.
    \item Active member of the Google Developers Group (\href{https://gdgsanaa.com/our-team/}{GDG Sana'a}), collaborating with a team of professionals to orchestrate and execute major events, including DevFest Sana'a \href{https://gdgsanaa.com/event/devfest-sanaa-2022/}{2022} and DevFest Sana'a \href{https://gdgsanaa.com/event/devfest-sanaa-2023/}{2023}. These initiatives served as platforms for fostering community participation, sharing knowledge, and promoting technological innovation.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS} 

\centering 
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.45\textwidth}>{\raggedright\arraybackslash}p{0.45\textwidth}@{}} 
    CCNA (2019) & General Telecommunication Institute (Sana'a)\\
    Google IT Support (2022) & By Google on \href{https://www.coursera.org/account/accomplishments/professional-cert/EDS5NDH9KCKP}{Coursera} \\
    Google Project Management (2023) & By Google on \href{https://www.coursera.org/account/accomplishments/professional-cert/LUEGUVMTTNHP}{Coursera} \\ 
    Python 3 Programming (2023) & By University of Michigan on \href{https://www.coursera.org/account/accomplishments/specialization/3RLDPNQXQHW8}{Coursera} \\
    Google IT Automation with Python (2023) & By Google on \href{https://www.coursera.org/account/accomplishments/professional-cert/HPRHTF393HDB}{Coursera} \\
    Google Cybersecurity (2024) & By Google on \href{https://www.coursera.org/account/accomplishments/professional-cert/HD8B8CUD5Y6K}{Coursera} \\
\end{tabular} 

\end{rSection}

\end{document}
